---
title: "Applied Marine Ecology - Problem Set 1"
author: "Kristin, Genevieve, and Roshni"
date: "1/6/2022"
output: 
   html_document:
     code_folding: hide 
     theme: cerulean
     toc: true
     toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
```

```{r}
ocean_data <- read_csv(here("data", "Data.csv"))
```

## Preparing the Data
```{r}
# original data
ocean_data <- read_csv(here("data", "Data.csv"))

# cleaning dataset 1
mean_density_adult <- ocean_data[6:18, ] %>% 
  row_to_names(1) %>% 
  clean_names() %>% 
  select(!c(na_2, na_3, na_4, na_5)) %>% 
  rename(organism = na) %>% 
  drop_na() %>% 
  rename(CI = each_sampling_date) %>% 
  mutate(organism = case_when(
    organism == "Surgeonfish (herbivores)" ~ "Surgeonfish",
    organism == "Coral Trout (predators of adult fishes)" ~ "Coral Trout",
    organism == "Spotted Damselfish (eats zooplankton)" ~ "Spotted Damselfish",
    organism == "Yellow Damselfish (eats zooplankton)" ~ "Yellow Damselfish",
    TRUE ~ organism
  ))

adult_2006 <- mean_density_adult %>% 
  select(organism, rarotonga, aitutaki, CI) %>% 
  mutate(CI = as.numeric(CI)) %>% 
  rename(Rarotonga = rarotonga) %>% 
  rename(Aitutaki = aitutaki) %>% 
  mutate(Rarotonga = as.numeric(Rarotonga)) %>% 
  mutate(Aitutaki = as.numeric(Aitutaki)) %>% 
  mutate(year = 2006)

adult_2022 <- mean_density_adult %>% 
  select(organism, rarotonga_2, aitutaki_2, CI) %>% 
  mutate(CI = as.numeric(CI)) %>% 
  rename(Rarotonga = rarotonga_2) %>% 
  rename(Aitutaki = aitutaki_2) %>% 
  mutate(Rarotonga = as.numeric(Rarotonga)) %>% 
  mutate(Aitutaki = as.numeric(Aitutaki)) %>% 
  mutate(year = 2022)

adult <- rbind(adult_2006, adult_2022)

adult_ci <- adult %>% 
  pivot_longer(cols = c(Rarotonga, Aitutaki), names_to = "location", values_to = "mean_density") %>% 
  mutate(ci_low = mean_density - CI) %>% 
  mutate(ci_high = mean_density + CI)
```

```{r}
# cleaning dataset 2

mean_number_new_young <- ocean_data[28:52, ] %>% 
  row_to_names(1) %>% 
  clean_names() %>% 
  select(!c(na_3, na_4, na_5)) %>% 
  rename(microhabitat = na_2) %>% 
  rename(fish = na) %>% 
  rename(CI = each_sampling_date) %>% 
  mutate(fish = row_number()) %>% 
  drop_na() %>% 
  mutate(fish = case_when(
    fish == c(2,3,4,5,6) ~ "Surgeonfish",
    fish == c(8,9,10,11,12) ~ "Coral Trout",
    fish == c(14,15,16,17,18) ~ "Spotted Damselfish",
    fish == c(20,21,22,23,24) ~ "Yellow Damselfish"
  ))

young_2006 <- mean_number_new_young %>% 
  select(fish, microhabitat, rarotonga, aitutaki, CI) %>% 
  rename(Rarotonga = rarotonga,
         Aitutaki = aitutaki) %>% 
  mutate(Rarotonga = as.numeric(Rarotonga)) %>% 
  mutate(Aitutaki = as.numeric(Aitutaki)) %>% 
  mutate(CI = as.numeric(CI)) %>% 
  mutate(year = 2006)

young_2022 <- mean_number_new_young %>% 
  select(fish, microhabitat, rarotonga_2, aitutaki_2, CI) %>%
  rename(Rarotonga = rarotonga_2) %>% 
  rename(Aitutaki = aitutaki_2) %>% 
  mutate(Rarotonga = as.numeric(Rarotonga)) %>% 
  mutate(Aitutaki = as.numeric(Aitutaki)) %>% 
  mutate(CI = as.numeric(CI)) %>% 
  mutate(year = 2022)

young <- rbind(young_2006, young_2022)

young_ci <- young %>% 
  pivot_longer(cols = c(Rarotonga, Aitutaki), names_to = "location", values_to = "mean_number") %>% 
  mutate(ci_low = mean_number - CI) %>% 
  mutate(ci_high = mean_number + CI) %>% 
  rename(organism = fish)

young_ci[young_ci==0] <- NA
```

## Question 1 - Adult Organisms

### Sugeonfish
```{r, fig.cap= "**Figure 1.**"}
surgeonfish_adult <- adult_ci %>% 
  filter(organism == "Surgeonfish")

ggplot(data = surgeonfish_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Surgeonfish") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Coral Trout
```{r, fig.cap= "**Figure 2.**"}
coral_trout_adult <- adult_ci %>% 
  filter(organism == "Coral Trout")

ggplot(data = coral_trout_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Coral Trout") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Spotted Damselfish
```{r, fig.cap= "**Figure 3.**"}
spotted_damselfish_adult <- adult_ci %>% 
  filter(organism == "Spotted Damselfish")

ggplot(data = spotted_damselfish_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Spotted Damselfish") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Yellow Damselfish
```{r, fig.cap= "**Figure 4.**"}
yellow_damselfish_adult <- adult_ci %>% 
  filter(organism == "Yellow Damselfish")

ggplot(data = yellow_damselfish_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Yellow Damselfish") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Mounding Corals
```{r, fig.cap= "**Figure 5.**"}
mounding_corals_adult <- adult_ci %>% 
  filter(organism == "Mounding Corals")

ggplot(data = mounding_corals_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Mounding Corals") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Coarse-Branching Corals
```{r, fig.cap= "**Figure 6.**"}
coarse_corals_adult <- adult_ci %>% 
  filter(organism == "Coarse-branching Corals")

ggplot(data = coarse_corals_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Area (m^2) of Coarse Corals per 100m^2 of Reef") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Fine-Branching Corals
```{r, fig.cap= "**Figure 7.**"}
fine_corals_adult <- adult_ci %>% 
  filter(organism == "Fine-branching Corals")

ggplot(data = fine_corals_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Area (m^2) of Fine Corals per 100m^2 of Reef") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Sea Anemones
```{r, fig.cap= "**Figure 8.**"}
sea_anemones_adult <- adult_ci %>% 
  filter(organism == "Sea Anemones")

ggplot(data = sea_anemones_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Area (m^2) of Sea Anemones per 100m^2 of Reef") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Algae
```{r, fig.cap= "**Figure 9.**"}
algae_adult <- adult_ci %>% 
  filter(organism == "Algae")

ggplot(data = algae_adult)+
  geom_col(aes(x = location, y = mean_density, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Area (m^2) of Algae per 100m^2 of Reef") +
  geom_errorbar(aes(x = location, y = mean_density, ymin = ci_low, ymax = ci_high), width = 0.2)
```

## Question 2 - Young Recruits

### Surgeonfish
```{r, fig.cap= "**Figure 10.**"}
surgeonfish_young <- young_ci %>% 
  filter(organism == "Surgeonfish") %>% 
  drop_na()

ggplot(data = surgeonfish_young)+
  geom_col(aes(x = location, y = mean_number, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Surgeonfish") +
  geom_errorbar(aes(x = location, y = mean_number, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Coral Trout
```{r, fig.cap= "**Figure 11.**"}
coral_trout_young <- young_ci %>% 
  filter(organism == "Coral Trout") %>% 
  drop_na()

ggplot(data = coral_trout_young)+
  geom_col(aes(x = location, y = mean_number, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Coral Trout") +
  geom_errorbar(aes(x = location, y = mean_number, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Spotted Damselfish
```{r, fig.cap= "**Figure 12.**"}
spotted_damselfish_young <- young_ci %>% 
  filter(organism == "Spotted Damselfish") %>% 
  drop_na()

ggplot(data = spotted_damselfish_young)+
  geom_col(aes(x = location, y = mean_number, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Spotted Damselfish") +
  geom_errorbar(aes(x = location, y = mean_number, ymin = ci_low, ymax = ci_high), width = 0.2)
```

### Yellow Damselfish
```{r, fig.cap= "**Figure 13.**"}
yellow_damselfish_young <- young_ci %>% 
  filter(organism == "Yellow Damselfish") %>% 
  drop_na()

ggplot(data = yellow_damselfish_young)+
  geom_col(aes(x = location, y = mean_number, fill = location))+
  facet_wrap(~year) +
  theme_minimal() +
  theme(legend.position ="none") +
  labs(x = "Location", y = "Mean Density of Yellow Damselfish") +
  geom_errorbar(aes(x = location, y = mean_number, ymin = ci_low, ymax = ci_high), width = 0.2)
```


## Question 3
```{r}
#Calculate the density of fish recruits per 100 m2 area of reef for each species

#SURGEONFISH
#convert density at 1m2 to density at 100m2 by creating a new column with the old value squared times 100?
surgeonfish_young_100m2 <- surgeonfish_young %>%
  mutate(mean_density_young = mean_number*mean_number*100) %>% 
  select(-c(ci_low, ci_high, CI, microhabitat, mean_number))

#remove variables from adult surgeonfish data frame
surgeonfish_adult_100m2 <- surgeonfish_adult %>% 
  select(-c(ci_low, ci_high, CI))

#merge young and adult data frames
young_old_surgeonfish <- merge(surgeonfish_adult_100m2, surgeonfish_young_100m2, by = c("year", "location", "organism"))

#calculate r^2 value
r2_surgeonfish <- lm(mean_density~mean_density_young, data=young_old_surgeonfish)
summary(r2_surgeonfish)$r.squared

#save csv (to double check r^2 value in excel)
#write.csv(young_old_surgeonfish, here("outputs", "young_old_surgeonfish2.csv"))

#CORAL TROUT
#convert density at 1m2 to density at 100m2 by creating a new column with the old value squared times 100?
ct_young_100m2 <- coral_trout_young %>%
  mutate(mean_density_young = mean_number*mean_number*100) %>% 
  select(-c(ci_low, ci_high, CI, microhabitat, mean_number))

#remove variables from adult surgeonfish data frame
ct_adult_100m2 <- coral_trout_adult %>% 
  select(-c(ci_low, ci_high, CI))

#merge young and adult data frames
young_old_ct <- merge(ct_adult_100m2, ct_young_100m2, by = c("year", "location", "organism"))

#calculate r^2 value
r2_ct <- lm(mean_density~mean_density_young, data=young_old_ct)
summary(r2_ct)$r.squared

#SPOTTED DAMSELFISH
#convert density at 1m2 to density at 100m2 by creating a new column with the old value squared times 100?
sd_young_100m2 <- spotted_damselfish_young %>%
  mutate(mean_density_young = mean_number*mean_number*100) %>% 
  select(-c(ci_low, ci_high, CI, microhabitat, mean_number))

#remove variables from adult surgeonfish data frame
sd_adult_100m2 <- spotted_damselfish_adult %>% 
  select(-c(ci_low, ci_high, CI))

#merge young and adult data frames
young_old_sd <- merge(sd_adult_100m2, sd_young_100m2, by = c("year", "location", "organism"))

#calculate r^2 value
r2_sd <- lm(mean_density~mean_density_young, data=young_old_sd)
summary(r2_sd)$r.squared

#YELLOW DAMSELFISH
#convert density at 1m2 to density at 100m2 by creating a new column with the old value squared times 100?
yd_young_100m2 <- yellow_damselfish_young %>%
  mutate(mean_density_young = mean_number*mean_number*100) %>% 
  select(-c(ci_low, ci_high, CI, microhabitat, mean_number))

#remove variables from adult surgeonfish data frame
yd_adult_100m2 <- yellow_damselfish_adult %>% 
  select(-c(ci_low, ci_high, CI))

#merge young and adult data frames
young_old_yd <- merge(yd_adult_100m2, yd_young_100m2, by = c("year", "location", "organism"))

#calculate r^2 value
r2_yd <- lm(mean_density~mean_density_young, data=young_old_yd)
summary(r2_yd)$r.squared
```

### Q3 Surgeonfish Plot
```{r}
#plot surgeonfish young vs old with R^2 value
ggplot(data = young_old_surgeonfish, aes(mean_density_young, mean_density))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 105000, y = 380, label = expression(~R^2~"= 0.404"))+
  labs(x = "Mean Density of Young Surgeonfish",
       y = "Mean Density of Adult Surgeonfish",
       title = expression("Mean Density of Young and Adult Surgeonfish Per 100"~m^2~"Area of Reef"))
```
### Q3 Coral Trout Plot
```{r}
#plot coral trout young vs old with R^2 value
ggplot(data = young_old_ct, aes(mean_density_young, mean_density))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 10000, y = 180, label = expression(~R^2~"= 0.876"))+
  labs(x = "Mean Density of Young Coral Trout",
       y = "Mean Density of Adult Coral Trout",
       title = expression("Mean Density of Young and Adult Coral Trout Per 100"~m^2~"Area of Reef"))
```

### Q3 Spotted Damselfish Plot
```{r}
#plot spotted damselfish young vs old with R^2 value
ggplot(data = young_old_sd, aes(mean_density_young, mean_density))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 21700, y = 870, label = expression(~R^2~"= 0.041"))+
  labs(x = "Mean Density of Young Spotted Damselfish",
       y = "Mean Density of Adult Spotted Damselfish",
       title = expression("Mean Density of Young and Adult Spotted Damselfish Per 100"~m^2~"Area of Reef"))
```

### Q3 Yellow Damselfish Plot
```{r}
#plot yellow damselfish young vs old with R^2 value
ggplot(data = young_old_yd, aes(mean_density_young, mean_density))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 150000, y = 90, label = expression(~R^2~"= 0.491"))+
  labs(x = "Mean Density of Young Yellow Damselfish",
       y = "Mean Density of Adult Yellow Damselfish",
       title = expression("Mean Density of Young and Adult Yellow Damselfish Per 100"~m^2~"Area of Reef"))
```


## Question 4
```{r}
#for each species make a scatterplot of the relationship between density of adults and density of microhabitat used by their young

#SURGEONFISH - density of adults and density of fine-branching coral
fbcoral_density <- adult_ci %>% 
  filter(organism == "Fine-branching Corals") %>% 
  select(-c(ci_low, ci_high, CI))

#merge adult surgeonfish density and fine-branching corals
surgeonfish_fbcoral <- merge(surgeonfish_adult_100m2, fbcoral_density, by = c("year", "location"))

#calculate r^2 value
r2_surgeonfish_fbcoral <- lm(mean_density.x~mean_density.y, data=surgeonfish_fbcoral)
summary(r2_surgeonfish_fbcoral)$r.squared

#CORAL TROUT - density of adults and density of course-branching coral
cbcoral_density <- adult_ci %>% 
  filter(organism == "Coarse-branching Corals") %>% 
  select(-c(ci_low, ci_high, CI))

#merge adult coral trout density and fine-branching corals
ct_cbcoral <- merge(coral_trout_adult, cbcoral_density, by = c("year", "location"))

#calculate r^2 value
r2_ct_cbcoral <- lm(mean_density.x~mean_density.y, data=ct_cbcoral)
summary(r2_ct_cbcoral)$r.squared

#SPOTTED DAMSELFISH - density of adults and density of sea anemones
sea_anemone_density <- adult_ci %>% 
  filter(organism == "Sea Anemones") %>% 
  select(-c(ci_low, ci_high, CI))

#merge adult spotted damselfish density and sea anemones
sd_sea_anemone <- merge(spotted_damselfish_adult, sea_anemone_density, by = c("year", "location"))

#calculate r^2 value
r2_sd_sea_anemone <- lm(mean_density.x~mean_density.y, data=sd_sea_anemone)
summary(r2_sd_sea_anemone)$r.squared

#YELLOW DAMSELFISH - density of adults and density of mounding coral
mounding_coral_density <- adult_ci %>% 
  filter(organism == "Mounding Corals") %>% 
  select(-c(ci_low, ci_high, CI))

#merge adult yellow damselfish density and mounding coral
yd_mounding_coral <- merge(yellow_damselfish_adult, mounding_coral_density, by = c("year", "location"))

#calculate r^2 value
r2_yd_mounding_coral <- lm(mean_density.x~mean_density.y, data=yd_mounding_coral)
summary(r2_yd_mounding_coral)$r.squared
```


### Q4 Surgeonfish Plot
```{r}
ggplot(data = surgeonfish_fbcoral, aes(x = mean_density.x, y = mean_density.y))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 310, y = 3.1, label = expression(~R^2~"= 0.965"))+
  labs(x = "Mean Density of Adult Surgeonfish",
       y = "Mean Density of Fine-branching Corals",
       title = expression("Mean Density of Adult Surgeonfish \nand Fine-branching Corals Per 100"~m^2~"Area of Reef"))
```

### Q4 Coral Trout Plot
```{r}
ggplot(data = ct_cbcoral, aes(x = mean_density.x, y = mean_density.y))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 120, y = 3.3, label = expression(~R^2~"= 0.776"))+
  labs(x = "Mean Density of Adult Coral Trout",
       y = "Mean Density of Course-branching Corals",
       title = expression("Mean Density of Adult Coral Trout \nand Course-branching Corals Per 100"~m^2~"Area of Reef"))
```
### Q4 Spotted Damselfish Plot
```{r}
ggplot(data = sd_sea_anemone, aes(x = mean_density.x, y = mean_density.y))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 750, y = 1.75, label = expression(~R^2~"= 0.948"))+
  labs(x = "Mean Density of Adult Spotted Damselfish",
       y = "Mean Density of Sea Anemone",
       title = expression("Mean Density of Adult Spotted \nDamselfish and Sea Anemone Per 100"~m^2~"Area of Reef"))
```

### Q4 Yellow Damselfish Plot
```{r}
ggplot(data = yd_mounding_coral, aes(x = mean_density.x, y = mean_density.y))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30")+ 
  theme_bw()+
  annotate("text", x = 85, y = 19.2, label = expression(~R^2~"= 0.000107"))+
  labs(x = "Mean Density of Adult Yellow Damselfish",
       y = "Mean Density of Mounding Corals",
       title = expression("Mean Density of Adult Yellow \nDamselfish and Mounding Corals Per 100"~m^2~"Area of Reef"))


```


## Question 5

```{r}
adult_microhabitat_old <- read_csv(here("data", "adult_microhabitat.csv"))

adult_microhabitat <- read_csv(here("data", "adult_density_young_microhabitat.csv"))

adult_microhabitat_2 <- read_csv(here("data", "adult_density_young_microhabitat_2.csv"))
```


### Surgeonfish 
```{r}
surgeonfish_adult_microhabitat <- adult_microhabitat_2 %>% 
  filter(organism == "Surgeonfish")

ggplot(data = surgeonfish_adult_microhabitat) + 
  geom_col(aes(x = location, y = adult_density_per_microhabitat, fill = location)) + 
  facet_wrap(~year) +
  theme_minimal() +
  labs(x = "Location", y = "Mean Density of Surgeonfish Per Fine-Branching Coral Area") +
  theme(legend.position ="none")
```


### Coral Trout
```{r}
coral_trout_adult_microhabitat <- adult_microhabitat_2 %>% 
  filter(organism == "CoralTrout")

ggplot(data = coral_trout_adult_microhabitat) + 
  geom_col(aes(x = location, y = adult_density_per_microhabitat, fill = location)) + 
  facet_wrap(~year) +
  theme_minimal() +
  labs(x = "Location", y = "Mean Density of Coral Trout Per Coarse-Branching Coral Area") +
  theme(legend.position ="none")
```


### Spotted Damselfish
```{r}
spotted_damselfish_adult_microhabitat <- adult_microhabitat_2 %>% 
  filter(organism == "SpottedDamselfish")

ggplot(data = spotted_damselfish_adult_microhabitat) + 
  geom_col(aes(x = location, y = adult_density_per_microhabitat, fill = location)) + 
  facet_wrap(~year) +
  theme_minimal() +
  labs(x = "Location", y = "Mean Density of Spotted Damselfish Per Sea Anemones Coral Area") +
  theme(legend.position ="none")
```


### Yellow Damselfish
```{r}
yellow_damselfish_adult_microhabitat <- adult_microhabitat_2 %>% 
  filter(organism == "YellowDamselfish")

ggplot(data = yellow_damselfish_adult_microhabitat) + 
  geom_col(aes(x = location, y = adult_density_per_microhabitat, fill = location)) + 
  facet_wrap(~year) +
  theme_minimal() +
  labs(x = "Location", y = "Mean Density of Yellow Damselfish Per Mounding Coral Area") +
  theme(legend.position ="none")
```


## Question 6 

For each pair of fish species, make an ‘XY(Scatter)’ plot (with linear trend line and R-square value) for the densities of adults (i.e., plot the densities of one species against another; you need to make 6 different graphs). Which show patterns and what are those trends?

### Surgeonfish vs Coral Trout 
```{r}





r2_surgeonfish <- lm(mean_density~mean_density_young, data=young_old_surgeonfish)
summary(r2_surgeonfish)$r.squared


ggplot(data = young_old_surgeonfish, aes(mean_density_young, mean_density))+
  geom_point()+
  geom_smooth(method = "lm", 
              se = FALSE, 
              color = "gray30") + 
  theme_bw() +
  annotate("text", x = 100000, y = 350, label = expression(~R^2~"= 0.404"))
  
```


### Surgeonfish vs. Spotted Damselfish 
```{r}

```


### Surgeonfish vs. Yellow Damselfish 
```{r}

```


### Coral Trout vs. Spotted Damselfish
```{r}

```


### Coral Trout vs. Yellow Damselfish
```{r}

```


### Spotted Damselfish vs. Yellow Damselfish
```{r}

```










